Lexicalized Domain Representations for Neural Machine Translation

### 2019-05-17 2019/emnlp/sparse.tex
rnn table

\begin{table*}
\begin{center}
 \begin{tabularx}{\textwidth}{|| X | X | X | X | X | X | X | X | X | X ||} 
 \hline
 Models & EMEA test & EMEA non-included & EPPS test & ECB test & khresmoi (EMEA domain) & test 2007 (EPPS domain) & newstest 2009 & newstest 2014 & IWSLT test 2010 \\ [0.5ex] 
 \hline\hline 
 Sparse - 4 & 74.65 & 49.61 & 37.42 & 54.49 & 33.68 & 31.01 & 20.71 & 28.03 & 25.28 \\
 \hline
 Sparse - 8 & 74.26 & 49.9 & 37.67 & 54.07 & 33.85 & 30.86 & 20.97 & 28.11 & 25.7 \\
 \hline
 Sparse - 16 & 74.15 & 49.1 & 37.78 & 54.56 & 33.4 & 30.93 & 20.73 & 28.1 & 25.33 \\
 \hline
 Sparse - 32 & 75.1 & 48.61 & 37.64 & 54.29 & 33.2 & 30.94 & 21.07 & 27.99 & 25.44 \\
 \hline
\end{tabularx}
\end{center}
\caption{BPE-detokenized BLEU score for English-French with the Transformer architecture}
\label{tab:5}
\end{table*}

>>>>

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc|}
\hline
$LDR$ & EMEA & EPPS & ECB & khreshmoi & newstest2014 & iwslt2010 \\
\hline
\multicolumn{7}{l}{English$\rightarrow$French} \\
\hline
 size=4   & 74.65 $_{49.61}$ & 37.42 & 54.49 & 33.68 & 28.03 & 25.28 \\
 size=8   & 74.26 $_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 \\
 size=16 & 74.15 $_{49.10}$ & 37.78 & 54.56 & 33.40 & 28.10 & 25.33 \\
 size=32 & 75.10 $_{48.61}$ & 37.64 & 54.29 & 33.20 & 27.99 & 25.44 \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the RNN architecture over test sets.}
\end{table*}
